---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simplr

<!-- badges: start -->

<!-- badges: end -->

⚠️ This package is under active development! Feedback is welcome, consistency is not yet promised.

## simple

*/ˈsɪmp(ə)l/*

adjective

comparative adjective: *simpler*

1\. easily understood or done; presenting no difficulty. "a simple solution"

Similar: `straightforward` `easy` `uncomplicated` `uninvolved` `effortless` `painless` `manageable` `undemanding` `unexacting` `elementary` `plain sailing`

Opposite: `difficult` `hard` `demanding` `complicated` `complex`

-   used to emphasize the fundamental and straightforward nature of something. "the simple truth"

The goal of simplr is to provide a few utility functions to make R usage a little simpler.

## Installation

You can install the development version of simplr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("vkatti/simplr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(simplr)
## basic example code
getStats(airquality)
```
